Motional Quantum Ground-State Cooling Outside the Lamb-Dicke Regime -- Supplemental material

### 2017-06-28 sm.tex
[SM] simulation results plots

>>>>

\subsection{Sample results}

\begin{figure}
  \includegraphics[width=8.5cm]{imgs/simcool_no_scatter.pdf}
  \caption{Simulated ground state population as a function of cooling cycles without
    technical imperfections \label{f-no-scatter}}
\end{figure}

\begin{figure}
  \includegraphics[width=8.5cm]{imgs/simcool_real.pdf}
  \caption{Simulated ground state population as a function of cooling cycles including effect of
    off-resonant scattering from all beams and OP misalignment\label{f-real}}
\end{figure}

When not considering the off-resonant scattering from the Raman beams and the tweezer as well
as optical pumping polarization misalignment, the simulation shows that there isn't a cooling
limit despite the large Lamb-Dicke parameter and high initial temperature (Fig \ref{f-no-scatter}).
However, when these effects are taken into account, the ground state probability can saturate at
a lower value (Fig \ref{f-real}) and require much more careful tweaking.
